DATA 621 Homework #3

### 2019-10-31 hw3/HW3.Rmd
Fixes and added description

### Feature Engineering
```{r}
library(fuzzyjoin)
density_diff <- function(data,eval_data,var,target,new_column){
  data[[paste0(var,"temp")]] <- data[[var]]
  eval_data[[paste0(var,"temp")]] <- eval_data[[var]]

@@

test<- density_diff(train,test,"nox",train$target,"nox_density")$new_data_eval
test<- density_diff(train,test,"age",train$target,"age_density")$new_data_training 
test<- density_diff(train,test,"indus",train$target,"indus_density")$new_data_training
test<- density_diff(train,test,"dis",train$target,"dis_density")$new_data_training
test<- density_diff(train,test,"rad",train$target,"rad_density")$new_data_training
test<- density_diff(train,test,"tax",train$target,"tax_density")$new_data_training
test<- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_training
test<- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_training
test<- density_diff(train,test,"medv",train$target,"medv_density")$new_data_training

@@

>>>>

### Feature Engineering
In this portion below we explored using the difference between the class distributions as a feature itself. So instead of the raw feature itself the we created density features that are essientially the differences in probability of the positve and negative classes at that certain point for the feature.

```{r}
library(fuzzyjoin)
density_diff <- function(data,eval_data,var,target,new_column){
  data[[paste0(var,"temp")]] <- data[[var]]
  eval_data[[paste0(var,"temp")]] <- eval_data[[var]]

@@

test<- density_diff(train,test,"nox",train$target,"nox_density")$new_data_eval
test<- density_diff(train,test,"age",train$target,"age_density")$new_data_eval
test<- density_diff(train,test,"indus",train$target,"indus_density")$new_data_eval
test<- density_diff(train,test,"dis",train$target,"dis_density")$new_data_eval
test<- density_diff(train,test,"rad",train$target,"rad_density")$new_data_eval
test<- density_diff(train,test,"tax",train$target,"tax_density")$new_data_eval
test<- density_diff(train,test,"ptratio",train$target,"ptratio_density")$new_data_eval
test<- density_diff(train,test,"lstat",train$target,"lstat_density")$new_data_eval
test<- density_diff(train,test,"medv",train$target,"medv_density")$new_data_eval

@@

### Example of the new meta feature
The first graph below is the difference between the distributions and the second graph is the new derived predictive feature
```{r}

density_diff(train,test,"age",train$target,"age_density")$dist
density_diff(train,test,"age",train$target,"age_density")$dist_diff
```
